---
title: 'Trends in the degree of control and treatment of cardiovascular risk factors in people with type 2 diabetes in the primary care setting in Catalonia during 2007-2018 '
author: "Jordi Real & Rai Puig"
website: "https://github.com/USR-DAPCAT/"

date: "`r format(Sys.time(), '%d %B, %Y')`"

output: 
  html_document:
    css: logos_css/usr_styles.css
    fig_caption: yes
    toc: yes
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
params:
   dir_dades_desti: "dades"
   website: https://github.com/USR-DAPCAT/
---
&nbsp;
<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"https://www.idiapjgol.org/images/logo.png\" style=\"float: right ;width: 130px;\"/>')
     $head.prepend('<img src=\"https://avatars2.githubusercontent.com/u/57066591?s=200&v=4\" style=\"margin-left:25% ;width: 80px;\"/>')
     $head.prepend('<img src=\"logos_css/logoDAP_Cat.png\" style=\"float: left:1;width: 185px;\"/>')
   });
</script>


<div class="watermark">DRAFT</div>

****

## 0. State:

**aggregations and descriptive global part**


&check; Trends in the degree of control and treatment of cardiovascular risk factors in people with type 2 diabetes in the primary care setting in Catalonia during 2007-2018 <br/>


**Pending**

&check; Review and debug errors.   <br/>



```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, include=F,size="huge")

gc()
#rm(list=ls())
library("dplyr")
library("lubridate")
library("trend")
library("Kendall")
library("HH")
library("purrr")
library("rstatix")
library("kableExtra")

# Funcions 
link_source<-paste0("https://github.com/jrealgatius/Stat_codis/blob/master/funcions_propies.R","?raw=T")
devtools::source_url(link_source)
directori_dades_origen<-params$dir_dades_origen

```

```{r llegir, include = FALSE}
#######################################################
# Llegir plana
dades<-readRDS(here::here(params$dir_dades_desti,"dt_poblacio.rds")) %>% as_tibble()
#dades1<-readRDS(here::here(params$dir_dades_desti,"dt_poblacio1.rds")) %>% as_tibble()
#dades_SupT1<-readRDS(here::here(params$dir_dades_desti,"dt_poblacio2.rds")) %>% as_tibble()
#dades_SupT2<-readRDS(here::here(params$dir_dades_desti,"dt_poblacio3.rds")) %>% as_tibble()

conductor<-here::here("conductor_Trend.xlsx")


# Filtrem  i ELIMINEM els Difunts anteriors al 20
#
#
#######################################################
```


```{r llegir_dades_formatades, include = FALSE}

#dades_format<-readxl::read_excel(here::here("dades","Trends.xlsx"),col_types ="text",sheet = "Tabla1_format") %>% as_tibble()

dades_format<-dades
#dades_format2<-dades_SupT1
#dades_format3<-dades_SupT2


dades_numeriques<-dades_format %>% filter(stringr::str_sub(tipo,1,1)=="n")
dades_qualis<-dades_format %>% filter(stringr::str_sub(tipo,1,1)=="Q")
#dades_qualis2<-dades_format2 %>% filter(stringr::str_sub(tipo,1,1)=="Q")
#dades_qualis3<-dades_format3 %>% filter(stringr::str_sub(tipo,1,1)=="Q")



```

```{r funcions, include=F}



calcul_p_trend<-function(dt=dades_qualis,var="Q4") {
  
  #dt=dades_qualis
  #var="Q4"
  
  lab<-dt %>% 
    filter(tipo==var)%>% 
    dplyr::select(NAMES)
  
  result<-
    dt %>% 
    filter(tipo==var) %>% 
    dplyr::select(starts_with("A")) %>% 
    mutate_all(as.numeric) %>% 
    prop_trend_test()
  
  if (result$p<0.001) {p<-"<0.001"} else p<-as.character(result$p)
  
   dplyr::distinct(tibble(variable=lab$NAMES,p_value=p,statistic=result$statistic,method=result$method))
   
  }






calcul_p_trend_mean<-function(dt=dades_numeriques,var="num1") {

  # dt=dades_numeriques
  # var="num1"
  
  year<-seq(2007,2018, by=1)
  
  N<-
    dt %>% 
    filter(tipo==var) %>% 
    dplyr::select(starts_with("C"))%>% 
    mutate_all(as.numeric)
  N<-as.numeric(N)
  
  mitjanes<-
    dt%>% 
    filter(tipo==var) %>% 
    dplyr::select(starts_with("A")) %>% 
    mutate_all(as.numeric)
  mitjanes<-as.numeric(mitjanes)
  
  sd<-
    dt%>% 
    filter(tipo==var) %>% 
    dplyr::select(starts_with("B")) %>% 
    mutate_all(as.numeric)
  sd<-as.numeric(sd)  
  
  PP2<-anovaMean(year,N,mitjanes,sd,ylabel=var,ans="summary.aov")
  
  lab<-dt %>% 
    filter(tipo==var)%>% 
    dplyr::select(NAMES)
  
  if (PP2$`Pr(F)`[1]<0.001) {p<-"<0.001"} else p<-as.character(PP2$`Pr(F)`[1])
  
  tibble(variable=lab$NAMES,p_value=p,F_Value=PP2$`F value`[1],Method="Anova 1 Factor")

  }


plot_t_trend<-function(dt=dades_numeriques,variable="num4") {

  #dt=dades_numeriques0
  #variable="num4"
  
  num<-dt %>% 
    filter(tipo==variable) %>% 
    dplyr::select(starts_with("A")) %>% 
    mutate_all(as.numeric) %>% as.numeric()
  year<-seq(2007,2018, by=1)

  dt2<-tibble(any=year,val=num)
  
  pvalor<-calcul_p_trend_mean(dt,variable) %>% pull(p_value) 
  
  etiqueta_var<-dt %>% filter(tipo==variable) %>% pull(NAMES)
  
  dt2 %>% ggplot(aes(any,val))  + geom_line() + geom_point() + 
    ggtitle(paste0(etiqueta_var, " during 2007-2018")) + 
    labs(caption=paste0("p-value=",pvalor))
    
  
  }




#%>%kable()
#  %>%kable_styling("striped",full_width=T)

#######################
#calcul_p_trend("Q3")##
#calcul_p_trend("Q2")##
######################

```



## 1. Descriptive Table 0
```{r Resultats0, include=T}


dades_qualis0<-dades_qualis %>%dplyr::filter(Suplements=="0")
dades_numeriques0<-dades_numeriques %>%dplyr::filter(Suplements=="0")



#i): quali
dades_qualis0%>%distinct(tipo) %>% pull(tipo) %>% 
  map_df(~calcul_p_trend(.x,dt=dades_qualis0)) %>% 
  kable() %>% kableExtra::kable_classic_2()

#ii): quanti
dades_numeriques0%>% distinct(tipo) %>% pull(tipo) %>% 
  map_df(~calcul_p_trend_mean(.x,dt=dades_numeriques0)) %>% 
  kable() %>% kableExtra::kable_classic_2()

#iii) quanti-plot!
dades_numeriques0%>% distinct(tipo) %>% pull(tipo) %>% 
 map(~plot_t_trend(.x,dt=dades_numeriques0)) 
  



```


## 1. Descriptive Table 1:[SupT1]
```{r Resultats1, include=T}


dades_qualis1<-dades_qualis %>%dplyr::filter(Suplements=="1")
#dades_numeriques1<-dades_numeriques %>%dplyr::filter(Suplements=="1")



#i): quali
dades_qualis1%>%distinct(tipo) %>% pull(tipo) %>% 
  map_df(~calcul_p_trend(.x,dt=dades_qualis1)) %>% 
  kable() %>% kableExtra::kable_classic_2()

#ii): quanti
#dades_numeriques1%>% distinct(tipo) %>% pull(tipo) %>% 
#   map_df(~calcul_p_trend_mean(.x,dt=dades_numeriques1))

#iii) quanti-plot!
#dades_numeriques1%>% distinct(tipo) %>% pull(tipo) %>% 
# map(~plot_t_trend(.x,dt=dades_numeriques1))



```

## 1. Descriptive Table 2:[SupT2]
```{r Resultats2, include=T}


dades_qualis2<-dades_qualis %>%dplyr::filter(Suplements=="2")

#dades_numeriques2<-dades_numeriques %>%dplyr::filter(Suplements=="2")



#i): quali
dades_qualis2%>%distinct(tipo) %>% pull(tipo) %>% 
  map_df(~calcul_p_trend(.x,dt=dades_qualis2))  %>% 
  kable() %>% kableExtra::kable_classic_2()

#ii): quanti
#dades_numeriques2%>% distinct(tipo) %>% pull(tipo) %>% 
#   map_df(~calcul_p_trend_mean(.x,dt=dades_numeriques2))

#iii) quanti-plot!
#dades_numeriques2%>% distinct(tipo) %>% pull(tipo) %>% 
# map(~plot_t_trend(.x,dt=dades_numeriques2))




```

## 1. Descriptive Table 3:[SupT3]
```{r Resultats3, include=T}



#dades_qualis3<-dades_qualis %>%dplyr::filter(Suplements=="3")
dades_numeriques3<-dades_numeriques %>%dplyr::filter(Suplements=="3")



#i): quali
#dades_qualis3%>%distinct(tipo) %>% pull(tipo) %>% 
#  map_df(~calcul_p_trend(.x,dt=dades_qualis3)) 

#ii): quanti
dades_numeriques3%>% distinct(tipo) %>% pull(tipo) %>% 
   map_df(~calcul_p_trend_mean(.x,dt=dades_numeriques3)) %>% 
   kable() %>% kableExtra::kable_classic_2()

#iii) quanti-plot!
dades_numeriques3%>% distinct(tipo) %>% pull(tipo) %>% 
 map(~plot_t_trend(.x,dt=dades_numeriques3))



```

## 1. Descriptive Table 4:[SupT4]
```{r Resultats4, include=T}

dades_qualis4<-dades_qualis %>%dplyr::filter(Suplements=="4")
#dades_numeriques4<-dades_numeriques %>%dplyr::filter(Suplements=="4")



#i): quali
dades_qualis4%>%distinct(tipo) %>% pull(tipo) %>% 
  map_df(~calcul_p_trend(.x,dt=dades_qualis4))%>% 
  kable() %>% kableExtra::kable_classic_2() 

#ii): quanti
#dades_numeriques4%>% distinct(tipo) %>% pull(tipo) %>% 
#   map_df(~calcul_p_trend_mean(.x,dt=dades_numeriques4))

#iii) quanti-plot!
#dades_numeriques4%>% distinct(tipo) %>% pull(tipo) %>% 
# map(~plot_t_trend(.x,dt=dades_numeriques4))


```



## 1. Descriptive Table 5:[SupT5]
```{r Resultats5, include=T}

dades_qualis5<-dades_qualis %>%dplyr::filter(Suplements=="5")
#dades_numeriques5<-dades_numeriques %>%dplyr::filter(Suplements=="5")


#i): quali
dades_qualis5%>%distinct(tipo) %>% pull(tipo) %>% 
  map_df(~calcul_p_trend(.x,dt=dades_qualis5))%>% 
  kable() %>% kableExtra::kable_classic_2() 

#ii): quanti
#dades_numeriques5%>% distinct(tipo) %>% pull(tipo) %>% 
#   map_df(~calcul_p_trend_mean(.x,dt=dades_numeriques5))

#iii) quanti-plot!
#dades_numeriques5%>% distinct(tipo) %>% pull(tipo) %>% 
# map(~plot_t_trend(.x,dt=dades_numeriques5))


```
## 1. Descriptive Table 6:[SupT6]
```{r Resultats6, include=T}


dades_qualis6<-dades_qualis %>%dplyr::filter(Suplements=="6")
#dades_numeriques6<-dades_numeriques %>%dplyr::filter(Suplements=="6")



#i): quali
dades_qualis6%>%distinct(tipo) %>% pull(tipo) %>% 
  map_df(~calcul_p_trend(.x,dt=dades_qualis6)) %>% 
  kable() %>% kableExtra::kable_classic_2()

#ii): quanti
#dades_numeriques6%>% distinct(tipo) %>% pull(tipo) %>% 
#   map_df(~calcul_p_trend_mean(.x,dt=dades_numeriques6))

#iii) quanti-plot!
#dades_numeriques6%>% distinct(tipo) %>% pull(tipo) %>% 
# map(~plot_t_trend(.x,dt=dades_numeriques6))



```

## 2. Save "Taula Plana"

```{r salvar}

#saveRDS(dades, file=here::here(params$dir_dades_desti,"dades.rds"))

```
&nbsp;
<hr />
<p style="text-align: center;">A work by $Jordi Real$ $Rai Puig$ </a></p>
<p style="text-align: center;">$Llepali System$ </a></p>
<p style="text-align: center;"><span style="color: #808080;"><em><https://github.com/USR-DAPCAT/></em></span></p>



